Flexible Scientific Data Management for Plant Phenomics Research

### 2013-03-11 s4biodiv2013/PODD-S4BIODIV-Submission.tex
add original PODD citation

In this paper, we expand on the design and implementation of the Phenomics
Ontology Driven Data repository [13] (PODD) with respect to the capture, storage
and retrieval of data and metadata generated at the High Resolution Plant
Phenomics Centre (Canberra, Australia). PODD is a schema-driven Semantic Web
database which uses the Resource Description Framework (RDF) model to store
semi-structured information. RDF allows PODD to process information about a
range of phenomics experiments without needing to define a universal schema for
all of the different structures. To illustrate the process, exemplar datasets
were generated using a medium throughput, high resolution, three-dimensional
digitisation system purposely built for studying plant structure and function
simultaneously under specific environmental conditions. The High Performance
Compute (HPC), storage and data collection publication aspects of the workflow
and their realisation in CSIRO infrastructure are also discussed along with
their relationship to PODD.

@@

References
[1] http://www.iucr.org/\_\_data/iucr/lists/epc-l/pdf00003.pdf
[2] http://topbraid.org/spin/api/
[3] http://www.plantontology.org/
[4] http://www.geneontology.org/
[5] https://wiki.csiro.au/confluence/display/dmsdoc/Home
[6] http://datatracker.ietf.org/doc/draft-kunze-bagit/
[7] https://pypi.python.org/pypi/bagit/
[8] http://sourceforge.net/projects/loc-xferutils/
[9] http://sourceforge.net/projects/loc-xferutils/files/loc-bagger/
[10] https://wiki.csiro.au/display/ASC
%[11] doi:10.1109/COINFO.2009.66 
%[12] doi:10.1016/j.jbi.2008.03.004
[13] doi:10.1007/978-3-642-13654-2\_22
[14] http://www.w3.org/DesignIssues/LinkedData.html

>>>>

In this paper, we expand on the design and implementation of the Phenomics
Ontology Driven Data repository \cite{Li2010} (PODD) with respect to the capture, storage
and retrieval of data and metadata generated at the High Resolution Plant
Phenomics Centre (Canberra, Australia). PODD is a schema-driven Semantic Web
database which uses the Resource Description Framework (RDF) model to store
semi-structured information. RDF allows PODD to process information about a
range of phenomics experiments without needing to define a universal schema for
all of the different structures. To illustrate the process, exemplar datasets
were generated using a medium throughput, high resolution, three-dimensional
digitisation system purposely built for studying plant structure and function
simultaneously under specific environmental conditions. The High Performance
Compute (HPC), storage and data collection publication aspects of the workflow
and their realisation in CSIRO infrastructure are also discussed along with
their relationship to PODD.

@@

References
[1] http://www.iucr.org/\_\_data/iucr/lists/epc-l/pdf00003.pdf
[2] http://topbraid.org/spin/api/
[3] http://www.plantontology.org/
[4] http://www.geneontology.org/
[5] https://wiki.csiro.au/confluence/display/dmsdoc/Home
[6] http://datatracker.ietf.org/doc/draft-kunze-bagit/
[7] https://pypi.python.org/pypi/bagit/
[8] http://sourceforge.net/projects/loc-xferutils/
[9] http://sourceforge.net/projects/loc-xferutils/files/loc-bagger/
[10] https://wiki.csiro.au/display/ASC
%[11] doi:10.1109/COINFO.2009.66 
%[12] doi:10.1016/j.jbi.2008.03.004
%[13] doi:10.1007/978-3-642-13654-2\_22
[14] http://www.w3.org/DesignIssues/LinkedData.html
